Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-21 awipev-CO2.Rmd
means of ph_s_sf_temp_insi and ph_s_dur_temp_fb calculated by grouping date rather than datetime

# Make mean for replicates. create separate seafet/durafet df to join to initial "d" df
pH_seafet_mean <- pH_seafet%>%
  dplyr::select(datetime, ph_s_sf_temp_insi)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(ph_s_sf_temp_insi = mean(ph_s_sf_temp_insi, na.rm = T))
pH_durafet_mean <- pH_durafet%>%
  dplyr::select(datetime, ph_s_dur_temp_fb)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(ph_s_dur_temp_fb = mean(ph_s_dur_temp_fb, na.rm = T))

>>>>

# Make mean for replicates. create separate seafet/durafet df to join to initial "d" df
pH_seafet_mean <- pH_seafet%>%
  dplyr::select(date, ph_s_sf_temp_insi)%>% 
  dplyr::group_by(date) %>% 
  dplyr::summarize(ph_s_sf_temp_insi = mean(ph_s_sf_temp_insi, na.rm = TRUE))
pH_durafet_mean <- pH_durafet%>%
  dplyr::select(date, ph_s_dur_temp_fb)%>% 
  dplyr::group_by(date) %>% 
  dplyr::summarize(ph_s_dur_temp_fb = mean(ph_s_dur_temp_fb, na.rm = TRUE))
